\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}

\usepackage{amsmath}
\usepackage{graphicx}

\usepackage{caption, subcaption, xcolor}

\graphicspath{{res/}}

\title{blimpy Test Coverage}
\author{Lukas Finkbeiner}

\begin{document}

\maketitle

\section{Introduction and Background}

\quad \quad The current test coverage of the blimpy repository, as reported by the dedicated shell script in the tests directory, is approximately 70\%. This represents the coverage specifically of a subset of scripts marked as active. The most obvious example of this is the deprecated folder: scripts which are being phased out are no longer tested for compatibility. 

Our current figures for code coverage represent an underestimate because there remains unused code which the tests mark as misses. The two primary examples of this are match\_fils.py and file\_wrapper.py. The code of match\_fils.py is largely dominated by a command-line utility which cannot be used outside of Green Bank machines. However, it is still tested by the testing script, so we generate artificial statement misses. Danny Price has recommended that this code be marked for deprecation. In the FilReader class in file\_wrapper.py, there are three unimplemented methods: read\_all, read\_row, and read\_rows. However, it is more accurate to call these unfinished since there is code in the body which is inaccessible because a NotImplementedError has been raised at the beginning of each.

Code exclusion is important, but the main purpose of this report is to document constructive improvements in test coverage. The current (and perhaps indefinite; see conclusion) emphasis of the tests appears to be the catching of run-time errors (i.e. script crashes) rather than logical errors (i.e. incorrect results). As a result, code coverage may sometimes be increased in such quick manners as simply calling a plotting routine. In other cases, it can require creative combinations of arguments to ensure that a routine raises the appropriate error.

Finally, there is another primary objective of this project which cannot be concisely measured here, but which is still open and significant to the maintenance of the repository. While surveying the existing tests, I discovered a general limitation in the quantity of specific documentation. I have been documenting my new test cases as I implement them. Documentation in the test cases benefits all future blimpy programmers. If a particular adjustment to the code causes the tests to fail, we want the programmer to immediately know which action failed. The shell will automatically report the name of the test method that failed, but without documentation in the method, one would have to study the code to learn or even relearn its conceptual purpose.

\section{Methods}

\quad \quad The blimpy repository includes two scripts necessary for running the complete suite of tests: download\_data.sh and run\_tests.sh. In this repository I have included two pared-down bash scripts, fast.sh and fail.sh. fail.sh is the fastest, but can only be used to check whether new test cases pass. fast.sh is the next fastest, and will check the coverage of all test scripts in the tests directory. Simpler bash scripts have the advantage of lower overhead, which allows the programmer to easily switch between writing tests and examining their impact. The principle downside of this pared-down approach is that fast.sh ignores repository warnings regarding which scripts are to be tested. Consequently, the programmer will receive coverage results about scripts in the directories `calib\_utils' and `deprecated' (observe the absence of such scripts from the tables below).

To further decrease the wait time (between writing and testing a test) I practice isolation on multiple layers. First, I move to a separate directory all scripts which I am not currently editing, so that the shell script will only run one test script at a time. For some of the slower scripts such as guppi.py (see `Current Efforts and Obstacles') I also isolate all test-functions except for the one I am currently developing. While the coverage numbers will decline in isolated testing environments, the programmer need only seek coverage increases $compared$ to the point at which isolation began.

On this topic, I have two recommendations for future test development. One is centralization, of which file\_wrapper.py is the worst offender. There is a dedicated test script, but if one runs this script by itself, the coverage for file\_wrapper.py decreases dramatically (by contrast, most other scripts will maintain roughly the same level of coverage for their tested script if you exclude the remaining tests). Test centralization is important because it facilitates the isolation approach. When isolating the file\_wrapper test script, the file\_wrapper coverage decreases so dramatically that one would lack a good sense of which tests were redundant; for example, one could add a function and notice a coverage increase, but that increase could evaporate when all tests are run together (some unnoticed lack of synergy between test cases). I have expanded test\_file\_wrapper.py to an extent which is not reflected in the coverage increases because I worked on enhancing the centralization of that script.

The second recommendation is compartmentalization. Within a testing script, there are several instances of single methods testing multiple features (for example, h5 and guppi file handling). If we focus on greater quantities of smaller methods which test discrete features, test failures will be easier to debug.

\section{Coverage Results}

\quad \quad The following table records the initial (as of February 2020) state of test coverage. It represents a view similar to what one will receive from running run\_tests.sh. I have shortened the script names unless the directory is necessary for disambiguation.

\begin{center}
 \begin{tabular}{||c c c c||} 
 \hline
 Script & Statements & Misses & Coverage (\%)\\ [0.5ex] 
 \hline
\_\_init\_\_ & 25 & 8 & 68 \\
\hline
bl\_scrunch & 45 & 25 & 44 \\
\hline
dice & 103 & 48 & 53 \\
\hline
ephemeris/\_\_init\_\_ & 3 & 0 & 100 \\
\hline
compute\_lsrk & 28 & 0 & 100 \\
\hline
compute\_lst & 15 & 4 & 73 \\
\hline
ephemeris/config & 9 & 2 & 78 \\
\hline
observatory & 41 & 12 & 71 \\
\hline
fil2h5 & 42 & 21 & 50 \\
\hline
guppi & 271 & 137 & 49 \\
\hline
h52fil & 42 & 21 & 50 \\
\hline
io/\_\_init\_\_ & 2 & 0 & 100 \\
\hline
fil\_writer & 41 & 8 & 80 \\
\hline
file\_wrapper & 397 & 101 & 75 \\
\hline
hdf\_writer & 87 & 20 & 77 \\
\hline
sigproc & 157 & 28 & 82 \\
\hline
match\_fils & 74 & 61 & 18 \\
\hline
plotting/\_\_init\_\_ & 7 & 0 & 100 \\
\hline
plotting/config & 11 & 2 & 82 \\
\hline
plot\_all & 69 & 5 & 93 \\
\hline
plot\_kurtosis & 16 & 2 & 88 \\
\hline
plot\_spectrum & 39 & 6 & 85 \\
\hline
plot\_spectrum\_min\_max & 44 & 5 & 89 \\
\hline
plot\_time\_series & 26 & 3 & 88 \\
\hline
plot\_utils & 28 & 4 & 86 \\
\hline
plot\_waterfall & 28 & 4 & 86 \\
\hline
utils & 65 & 0 & 100 \\
\hline
waterfall & 228 & 57 & 75 \\
\hline
&&&
\\
\hline
TOTAL & 1925 & 581 & 70 \\ [1ex] 
\hline
\end{tabular}
\end{center}

In this next table, I report the details of scripts for whom testing has increased. The precise numbers are accurate as of the writing of this report.

\begin{center}
 \begin{tabular}{||c c c c||} 
 \hline
 Script & Misses & Decrease & Latest Coverage (\%)\\ [0.5ex] 
\hline
bl\_scrunch & 25 & 12 & 72 \\
\hline
dice & 38 & 10 & 63 \\
\hline
fil2h5 & 8 & 13 & 82 \\
\hline
guppi & 77 & 60 & 72 \\
\hline
h52fil & 8 & 13 & 82 \\
\hline
file\_wrapper & 66* & 17 & 83* \\
\hline
match\_fils & 0* & 10 & 100* \\
\hline
waterfall & 51 & 6 & 78 \\
\hline
&&&
\\
\hline
TOTAL$^\dagger$ & 403 & 178 & 79 \\ [1ex] 
\hline
\end{tabular}
\end{center}

The asterisks indicate fields for which I am factoring-in the deprecations and exclusions that I mention in the `Concluding Recommendations' section. The dagger indicates that the total includes numbers from the tests which were not shown (because their coverage had not changed).

%axe 35

\section{Current Efforts and Obstacles}

\quad \quad The guppi file-handling script guppi.py represented a thorn in the side of this project. Operation of this script was especially slow. On many occasions, even running tests on this script in isolation, the code-coverage routine would experience a time-out, killing the test session. In visually analyzing the script, I have not come across many areas which could be rewritten up to resolve this issue. However, virtually all of the user-facing methods (e.g. histogram) deplete the file. As a consequence, each test case must create a new guppi-handler object from scratch. This places a major strain on the hard disk, the slowest piece of a computer.

One ongoing project is the accessing of command-line tools for testing purposes. Several scripts such as bl\_scrunch and h52fil come packaged with methods which allow the user to analyze and plot data by passing in arguments directly from the shell. All such functions include a line which relies on an external dependency to parse console inputs. guppi.py has such a tool, but it also features a parameter in the method header should the programmer wish to access the tool from a script. I have been modifying the blimpy scripts so that more of the command line methods have this feature; it allows the test scripts to easily enter different inputs.

Some issues are broader in scope and arguably not well suited for a nuts-and-bolts project such as this, or at least for an intern with less experience with the long term aims and priorities of the repository as a whole. For example, virtually all of the test cases rely on a set of Voyager data in the .h5 and .fil formats. We are essentially using a single source for all tests. Consequently, there are many if statements which are not executed because they bifurcate around properties specific to the file's data type (small integers, large integers, or floats), number and sizes of channels, etc.

This gets into an issue of diminishing returns. Introducing entire additional data sets will undoubtedly slow down the testing process, even using the isolation approach that I described in the methods section.

\section{Concluding Recommendations}

\quad \quad In conclusion, some quick and large improvements in code coverage would come from excluding the appropriate sections of the code, which are not in use. We need to deprecate the command-line tool in match\_fils.py and we need to formally exclude the incomplete methods in file\_wrapper.py.

Depending on the popularity of guppi.py, streamlining will vary as a priority. Currently, however, the script represents a major bottleneck when trying to test the entire repository at once. At the very least, I learned that the generate\_filterbank\_header method relies on several hard-coded and other un-calculated quantities: in any case, the script is unfinished. There seem to be several methods with comments recommending relocation to a plotting script. This could be a promising near-future tactic for circumventing the file depletion exacerbation of disk reads.

Finally, there remain philosophical issues on the horizon. The routes of continuation for this project are fairly straightforward for the short term. However, as we approach near-total coverage of blimpy for runtime errors and documentation of tests, the question of logical errors may become more relevant. As mentioned in the introduction, there are only a few tests that test to make sure that the outputs are what we expect them to be. If this issue ever becomes more of a testing priority, there will be great time demands as we seek to independently calculate the values that we expect from blimpy.

\end{document}
